### 2020-02-02 article.tex
Sections descriptions added at the end of the introduction

>>>>

The rest of this paper is organized as follows. Participant and dataset information, pre-processing steps, tools and materials used, and the proposed method are described respectively in Section \ref{section:materials}. Experiments and results can be seen in Section \ref{section:results}. Conclusion and discussion can be found in Section \ref{section:discussion}. Finally, Section \ref{section:future} contains the limitations and future directions.
